Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (standardised Multivariate Normal distribution)

### 2022-06-24 Manual.Rmd
updated manual title spelling mistakes

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for PoissonRegression (standardised Multivariate Normal Distribution)"
output: github_document
---

@@

* The project ***"Normal_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Normal"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the Poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.

@@

* Based on the real model of the Poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Normal_Special.R***.

@@

* For each model structure covariate data was generated only through zero covariance matrices with mean of zeros from the Multivariate Normal distribution.

@@

#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]

>>>>

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (standardised Multivariate Normal distribution)"
output: github_document
---

@@

* The project ***"Normal_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Normal"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.

@@

* Based on the real model of the poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Normal_Special.R***.

@@

* For each model structure covariate data was generated only through standardised Multivariate Normal distribution.

@@

#### 2.2.1.5 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]
